
<!---BLOCK_LANDSCAPE_START--->

# Quota (%) table after transition period (Year 10)

```{r FinalQuotaAllocationTable}
kable(QUOTA_TABLE_FORMATTED, align = c("l", "l", "l", "c", "r", "r", "r", "r"))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# TAC (metric tonnes; t) table after transition period (Year 10)

```{r FinalTACAllocationTable}
kable(TAC_TABLE_FORMATTED, align = c("l", "l", "l", "c", "r", "r", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# Baseline allocation for Contracting Parties

```{r BaselineAllocationTable}
kable(BA_ALLOCATION_TABLE_FORMATTED, align = c("l", "l", "l", "c", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# Coastal state allocation

## Equal allocation

```{r CoastalStateAllocationEqualTable, ft.align = "center"}
kable(CS_EQUAL_ALLOCATION_TABLE_FORMATTED, align = c("l", "l", "l", "c", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

## Socio-economic allocation

### Human Development Index status allocation

```{r CoastalStateAllocationSEHDITable}
kable(CS_SE_HDI_ALLOCATION_TABLE_FORMATTED, align = c("l", "l", "l", "c", "c", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

### Gross national income status allocation

```{r CoastalStateAllocationSEGNITable}
kable(CS_SE_GNI_ALLOCATION_TABLE_FORMATTED, align = c("l", "l", "l", "c", "c", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

### Small Islands Development status allocation

```{r CoastalStateAllocationSESIDSTable}
kable(CS_SE_SIDS_ALLOCATION_TABLE_FORMATTED, align = c("l", "l", "l", "c", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

## National Jurisdiction Area allocation

```{r CoastalStateAllocationNJATable}
kable(CS_NJA_ALLOCATION_TABLE_FORMATTED, align = c("l", "l", "l", "c", "r", "r", "r"), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# Catch-based allocation (%)

```{r CatchBasedQuotaAllocationTable}
kable(CB_ALLOCATION_QUOTAS_ALL_YEARS_TABLE_FORMATTED, align = c("l", "l", "l", "c", rep("r", 10)))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# Catch-based allocation (metric tonnes)

```{r CatchBasedTACAllocationTable}
kable(CB_ALLOCATION_TACS_ALL_YEARS_TABLE_FORMATTED, align = c("l", "l", "l", "c", rep("r", 10)), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# Total allocation (%)

```{r TotalQuotaAllocationTable}
kable(ALLOCATION_QUOTAS_ALL_YEARS_TABLE_FORMATTED, align = c("l", "l", "l", "c", rep("r", 10)), format.args = list(big.mark = ","))
```

```{r, results='asis',message=FALSE, warning=FALSE, comment=FALSE,echo=FALSE}
if(is.null(REPORTING_ENTITY)) pagebreak()
```

# Total allocation (metric tonnes)

```{r TotalTACAllocationTable}
kable(ALLOCATION_TACS_ALL_YEARS_TABLE_FORMATTED, align = c("l", "l", "l", "c", rep("r", 10)), format.args = list(big.mark = ","))
```

<!---BLOCK_LANDSCAPE_STOP--->
