---
title: "Simulation Tool for Allocation Criteria: Data, Assumptions and Outputs (Updated Version)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  officedown::rdocx_document:
    reference_docx: "./templates/rdoc_template.docx"
reference_num: TRUE
fig_caption: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      tab.cap.pre = "Tab. ", 
                      tab.cap.sep = ". ", 
                      tab.cap.style = "Table Caption", 
                      tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE), 
                      fig.cap = TRUE, 
                      fig.cap.pre = "Fig. ", 
                      fig.cap.sep = ". ", 
                      fig.cap.style = "Caption label",
                      dpi = 300
)
```

```{r Headers, echo = FALSE}
logo.file = file.path("./templates/FAO_IOTC_LOGOS.png")

bl_header_no_logo = function(txt, position) {
  block_list(
    fpar(values = txt, fp_p = fp_par(text.align = position, border.bottom = fp_border()), fp_t = fp_text_lite(color = "black", bold = FALSE, font.size = 12))
  )
}

bl_header_with_logo = function(txt, position) {
  block_list(
    fpar(external_img(src = logo.file, height = 0.71, width = 7.19, unit = "in"), 
    ftext = txt, 
         fp_p = fp_par(text.align = position, border.bottom = fp_border()), 
         fp_t = fp_text_lite(color = "black", bold = FALSE, font.size = 12)))
}

footer_test = block_list(fpar(run_word_field(field = "PAGE  \\* ARABIC"),
                                  fp_p = fp_par(text.align = "center")))


sec_pr = prop_section(
  header_first = bl_header_with_logo("IOTC-2026-TCAC16-INF01", "right"),
  header_even = bl_header_no_logo("IOTC-2026-TCAC16-INF01", "right"), 
  header_default = bl_header_no_logo("IOTC-2026-TCAC16-INF01", "right"), 
  footer_default = footer_test, 
  footer_even = footer_test, 
  footer_first = footer_test
)

```

```{r TextStyles, echo = FALSE, eval = TRUE}
fp = fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

alert = fp_text(shading.color = "transparent", bold = TRUE, color = "red")
underline = fp_text(underlined = TRUE)
```

```{r eval = TRUE}
block_section(sec_pr)
```

# Summary

This paper describes the data, assumptions and outputs underpinning the updated simulation tool developed by the IOTC Secretariat to support the work of the Technical Committee on Allocation Criteria (TCAC). It documents the analytical framework used to simulate alternative catch allocation scenarios, including the treatment of entities, historical catch data, national jurisdiction areas and allocation components.

The paper outlines the input datasets used in the simulations, notably the entity reference dataset and historical catch estimates by fishing area, and explains key assumptions applied for analytical consistency, including the treatment of disputed maritime areas and non-IOTC jurisdictions. While the simulation framework has been updated since TCAC15, the historical catch series currently used remain those considered at that session, pending the finalisation of ongoing data revisions.

The document also describes the interactive R Shiny application developed to allow TCAC members to configure and explore allocation scenarios, including options for setting Total Allowable Catch values, allocation weights, reference periods and transition periods. Finally, it summarises the types of outputs generated by the tool, including tables, charts and downloadable Excel and Word reports, provided either for all entities or individually.


```{r child = "06_01_Purpose.Rmd"}
```

```{r child = "06_02_Inputs.Rmd"}
```

```{r child = "06_03_Simulations.Rmd"}
```

```{r child = "06_04_Results.Rmd"}
```

\pagebreak

```{r child = "06_Appendix_01_Entity_Data.Rmd"}
```

\pagebreak

```{r, echo = F}
block_section(sec_pr)
```

```{r child = "06_Appendix_02_Catch_Data.Rmd"}
```

